Modal Abstractions for Virtualizing Memory Addresses

### 2023-02-21 programlogic.tex
+

>>>>

One possible approach to resolving this is to identify and separate the type of ownership within and outside the virtual points-to relation. Iris has a ghost map resource where authoritative ownership of an individual key-value pair can be handled as a resource. We use this mechanism to separate the virtual-to-physical translation from the physical memory involved: (fractional) virtual points-to assertions can be defined in terms of (fractional) ownership of these authoritative ghost map entry assertions, plus sharing an in-variant that the current installed page table respects all entries of the mapping as shown in Figure. Unmapping collects the authoritative map kvpairs from collecting the assertions, and then can remove them from the ghost map and update the page tables. Critically, physical ownership of the page tables then lives in the invariant on the current page table, so some virtual pointsto as- sertions can refer to memory in those page tables. This still works with the modality, since that invariant is also semantically a predicate on a page table root.
